Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-10-17 psy_peds_3.Rmd
update Rmd code to plot specific disorder subgroups

```{r message=FALSE, warning=FALSE}
folder_4ce_files <- "Input/09212021_2/"
obfuscation =  FALSE
#obfuscation = 3
raceAvailable = TRUE
#raceAvailable = FALSE
dateFormat <- "%d-%b-%y"
min_hosp_days <- 2
data_update_date <- "2021-06-05"
time_period <-"months" #possible values: days, weeks, months
```

@@

@@

dgPerc
```

>>>>

```{r message=FALSE, warning=FALSE}
folder_4ce_files <- "../Input/09212021_2/"
obfuscation =  FALSE
#obfuscation = 3
raceAvailable = TRUE
#raceAvailable = FALSE
dateFormat <- "%d-%b-%y"
min_hosp_days <- 2
data_update_date <- "2021-06-05"
time_period <-"months" #possible values: days, weeks, months
```

@@

#### Subset: the most prevalent disorder group
```{r}
dg_subset <- count_disorder_group %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" )) %>%
  ggplot(aes(x = time_p, y= count_dg, fill = period, group = disorder_group )) +
  geom_bar(stat = "identity")+
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se= TRUE, aes(colour=period), colour= "black", size = 0.5) + 
  labs(x = time_period,
       y = "Patient Count",
       title = paste0("Per ", time_period, " patient counts with mental health related ICD codes"), 
       subtitle = "Grouped by mental health ICD subcategories") + 
  ylim(0, NA) + 
  facet_wrap(. ~ disorder_group, scales = "free_y") +
  theme(strip.text.x = element_text(size = 12),
        axis.text.x = element_text(size = 12, angle = 90), 
        axis.text.y = element_text(size = 11), 
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 11),
        title = element_text(size = 12),
        plot.subtitle = element_text(size = 11),
        legend.position = "none") +
  scale_fill_manual(values = cbPalette[-1])

dg_subset
```

@@

dgPerc
```
```{r}
dgPerc_subset <- perc_disorder_group %>%  
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" )) %>%
  ggplot(aes(x = time_p, y= percentage_dg, fill = period, group = disorder_group )) +
  geom_bar(stat = "identity")+
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se= TRUE, aes(colour=period), colour= "black", size = 0.5) + 
  labs(x = time_period,
       y = "Patient (%)",
       title = paste0("Percentage of patients per ", time_period,"with mental health related ICD codes"), 
       subtitle = "Grouped by mental health ICD subcategories") + 
  ylim(0, NA) + 
  facet_wrap(. ~ disorder_group, scales = "free_y") +
  theme(strip.text.x = element_text(size = 12),
        axis.text.x = element_text(size = 12, angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        title = element_text(size = 12),
        plot.subtitle = element_text(size = 11),
        legend.position = "none") +
  scale_fill_manual(values = cbPalette[-1])

dgPerc_subset
```
